---
title: "GEE Comparison"
author: "Jon Ong"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls()); gc()
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(gee, geepack, dplyr, data.table)
load("Output/batch0316.rda")

checkdiff<- function(listA, listB){
  convergeID_A<- !sapply(listA, anyNA)
  convergeID_B<- !sapply(listB, anyNA)
  convergeID <- which(convergeID_A * convergeID_B ==1)
  A<- lapply(convergeID, function(i) listA[[i]]) %>% do.call(rbind,.)
  B<- lapply(convergeID, function(i) listB[[i]]) %>% do.call(rbind,.)
  DIFF<- A-B

  par(mfrow=c(1,2))
  hist(DIFF[,1], main= "Difference in mean estimates", xlab = "GEEPACK - GEE")
  hist(DIFF[,2], main= "Difference in se estimates", xlab = "GEEPACK - GEE")
  cat("number of convergence:" , length(convergeID), "out of", length(listA),"\n\n")
  summary(DIFF[,c(1,2)]) %>% return
}
```

## Simulation Setup

|      | iter | n   | p   | QELR Param |
|------|------|-----|-----|------------|
| Sim1 | 500  | 300 | 3   | V1         |
| Sim2 | 500  | 300 | 3   | V2         |
| Sim3 | 500  | 300 | 5   | V3         |
| Sim4 | 500  | 300 | 10  | V4         |
| Sim5 | 500  | 300 | 12  | V5         |

Remarks:

1.  I've excluded the "unstructured" correlation structure from simulation.

2.  In terms of gee parameters:

    1.  Maxiter: Manually increased maxiter to a large number (eg. 200), when working correlation is not independent.

    2.  Scale.fixed: Sometimes solutions would converge when scale.fixed = TRUE (default = FALSE). Currently set as FALSE

3.  GEE package: only used the sandwich estimator’s result (Robust variance)

```{r}
allout$V1 %>% round(.,2)
allout$V2 %>% round(.,2)
allout$V3 %>% round(.,2)
allout$V4 %>% round(.,2)

```

## Differences Between GEE and GEEPACK: Do both packages generate the same estimates?

Short answer: YES for independence correlation.

GEE stops and returns an error message when solution diverges, however GEEPACK would still produce (erroneous, some extremely large values) estimates.

The below analysis answers a few questions to address the comparison/ differences:

1.  Out of 500 simulations, how many converged solutions do we get?

```{r}
rbind(sim1= sapply(allout$sim1$convergecase, sum), 
      sim2= sapply(allout$sim2$convergecase, sum), 
      sim3= sapply(allout$sim3$convergecase, sum)) %>% t()
```

1.  Distribution of the differences between GEE and GEEPACK estimates (among the converged cases)?

    ##### Sim1

    1.  Independence correlation shows negligible differences.
    2.  Exchangeable correlation shows noticeable differences. This refers to the 72 converged cases from "GEE". Could it be that GEEPACK and GEE yield different divergence/ convergence cases? Further deep dive can be done here.
    3.  AR-1: only 1 converged case here, no comment.

```{r, echo= TRUE}
checkdiff(allout$sim1$OUT$geepack_ind, allout$sim1$OUT$gee_ind)
checkdiff(allout$sim1$OUT$geepack_exc, allout$sim1$OUT$gee_exc)
checkdiff(allout$sim1$OUT$geepack_ar1, allout$sim1$OUT$gee_ar1)
```

##### Sim2

1.  Independence correlation shows negligible differences.
2.  Exchangeable correlation shows noticeable differences in both packages, using the 490 converged cases from GEE.
3.  AR-1: 0 converged case here, no comparison/ comment.

```{r}
checkdiff(allout$sim2$OUT$geepack_ind, allout$sim2$OUT$gee_ind)
checkdiff(allout$sim2$OUT$geepack_exc, allout$sim2$OUT$gee_exc)
#checkdiff(allout$sim2$OUT$geepack_ar1, allout$sim2$OUT$gee_ar1) # no convergence cases


```

##### Sim3

1.  Independence correlation shows negligible differences.
2.  Exchangeable correlation shows noticeable differences in both packages, using the 93 converged cases from GEE.
3.  AR-1: 0 converged case here, no comparison/ comment.

```{r}
checkdiff(allout$sim3$OUT$geepack_ind, allout$sim3$OUT$gee_ind)
checkdiff(allout$sim3$OUT$geepack_exc, allout$sim3$OUT$gee_exc)
#checkdiff(allout$sim3$OUT$geepack_ar1, allout$sim3$OUT$gee_ar1) # no convergence cases

```

## Differences across different working correlations: Do all correlation structures generate the same estimates?

This can be answered by checking the bias and relative s.e:

1.  Independence correlation: already proved from previous simulation that it guarantees good estimates for parameters.
2.  Exchangeable correlation: poor estimates basedon the converged results from GEE.
3.  AR1 correlation: almost no convergence, hence no comment.

##### Sim1 

```{r, echo = FALSE}
allout$sim1$K$gee_ind %>% round(.,4)
allout$sim1$K$gee_exc %>% round(.,4)
```

##### Sim2

```{r, echo = FALSE}
allout$sim2$K$gee_ind %>% round(.,4)
allout$sim2$K$gee_exc %>% round(.,4)
```

##### Sim3

```{r, echo = FALSE}
allout$sim3$K$gee_ind %>% round(.,4)
allout$sim3$K$gee_exc %>% round(.,4)
```
